The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-13 paper/thingap_ref_response/response_to_referee.tex

\item With regard to saturation through modification of the base flow, in the TC problem studied in these papers, the rotation law is enforced through viscous coupling of the interior fluid to the bounding cylinders. This introduces a timescale, the viscous diffusion time, with which the momentum transport driven by perturbations must compete. In an accretion disk the rotation law is enforced at every point directly by gravity. The authors should comment on how important they think this difference is to saturating the mode.

\textbf{In Paper II, the rotation law is enforced through viscous coupling to the boundaries. In Paper I, however, the rotation law is imposed directly at every point by the shear. We have noted this point in the text. See also the newly extended discussion of the local flow with shear periodic boundary conditions.}

\item The influence of boundary conditions and boundary layers is strong. To call out some examples: In Paper I, the amplitude $\alpha$ converges to the constant value $(b/c)^{1/2}$, independent of z. Is this really relevant to a lab experiment with vertical endcaps, or to a stratified disk? Have the authors experimented with a finite cylinder, even a very tall one? Likewise, the radial boundaries seem to play a role that a softer physical boundary might not, for example the boundary layers in Figure 2 of Paper II (in this case it would be useful to show blowups of the solution, as in Figure 4, and present evidence for numerical convergence). I would like to see more discussion of the role of these boundary conditions versus physical boundary conditions. Again, it is OK to model a lab experiment – but the connection to a natural system should be kept in mind.

\textbf{The amplitude $\alpha$ is bounded by the value +/- $(b/c)^{1/2}$, although the amplitude does not necessarily converge to a constant value, as shown in Figures 6 and 7. We note, however, that although the value of the quantity $(b/c)^{1/2}$ is heavily influenced by the boundary layers in the walled TC flow, this is specific to the wall-like boundary conditions and not inherent to the theory. We have added a paragraph at the end of section 4 to elaborate on this point, discuss what the $(b/c)^{1/2}$ saturation amplitude means physically, and describe how the derived amplitude applies to the shearing box MRI.}

### 2017-03-13 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
for numerical convergence plot
replaced beta with Co

\newcommand\reye{\mathrm{Re}}
\newcommand\reym{\mathrm{Rm}}
\newcommand{\Pm}{\mathrm{Pm}}

@@

We note several other important analytical studies of MRI saturation. \citeauthor{Knobloch:2005ba} (\citeyear{Knobloch:2005ba}) analyze the MRI in the strongly nonlinear regime, by following the already-developed MRI modes into asymptotic saturation. They consider a thin-gap regime as well, and so their theory may be considered the strongly nonlinear analogue to the one developed here. \citet{Vasil:2015} examines the weakly nonlinear MRI in a thin-gap regime in a minimal model, finding deep mathematical similarities between the MRI system and the elastodynamic instability of a buckling beam. We discuss these results and their relation to ours in section~\ref{sec:discussion}. Several authors have investigated the behavior of the MRI when the boundary conditions are shear periodic, and so the MRI has no mechanism by which to modify the background shear flow profile. In this approximation linear MRI growth is dominated by channel modes, a type of MRI mode that, for periodic boundary conditions, are exact solutions of both the linear and nonlinear MRI equations \citep{Goodman:1994ul}. In this regime the MRI saturates via parasitic instabilities, which feed off and destroy the primary MRI modes. Analytical investigation of this case reveals that MRI saturation can be caused by parasitic Kelvin-Helmholtz and tearing mode instabilities, depending on parameter regime \citep{Pessah:2010ic}. The theory of MRI channel mode parasites is robust \citep[see also]{Pessah:2009gm;Latter:2010iz;Rembiasz:2016}, but their importance may be overestimated by the local approximation \citep{Latter:2015}, and not germane to global analyses like the one presented here. \citet{Latter:2015} gives a detailed analysis of the relation between local and global linear MRI modes.

@@

We axisymmetrically perturb all three vector components of each of the fluid quantities. We nondimensionalize the equations, with lengths nondimensionalized by $L$, time by $\Omega_0$, velocities by $\Omega_0 L$, magnetic fields by $B_0$, and pressure by $\Omega_0^2 L^2 \rho_0$, where $L$ is the channel width, $\Omega_0$ is the rotation rate at the center of the channel, and $\rho_0$ is the constant pressure in the base state (see Figure \ref{fig:setup}). We define the Reynolds number, $\reye \equiv {\Omega_0 L^2}/{\nu}$, magnetic Reynolds number, $\reym \equiv {\Omega_0 L^2}/{\eta}$, and a plasma beta parameter, $\beta \equiv {\Omega_0^2r_0^2}/{v_A^2}$, where the Alfv\'en speed $v_A$ is $v_A^2 = {B_0^2}/{\rho_0}$. The fluid symbols $\mathbf{u}$, $\mathbf{B}$, etc. will henceforth be used to refer to the nondimensional, perturbed quantities.

@@

%\begin{widetext}
\onecolumngrid
\beq
\label{eqset1}
\partial_t \nabla^2 \Psi \, - \, 2 \partial_z u_{y} \, - \, \frac{2}{\beta} B_0 \partial_z \nabla^2 A \, - \, \frac{1}{\reye}\nabla^4 \Psi \, = \, \frac{2}{\beta}J\left(A, \nabla^2 A \right) \, - \, J\left(\Psi, \nabla^2 \Psi\right) \, 
\eeq
%\end{eqnarray}
%\end{widetext}

\beq
\label{eqset2}
\partial_t u_{y} \, + \, \left(2 - q\right) \Omega_0 \partial_z \Psi \, = \, \frac{2}{\beta}B_0\partial_z B_{y} \, + \, \frac{2}{\beta} J\left(A, B_{y}\right) \, - \, J\left(\Psi, u_{y}\right) \, + \, \frac{1}{\reye} \nabla^2 u_{y}
\eeq

@@

The weakly nonlinear regime is where the MRI system is nonlinearly unstable to only the most unstable mode of the linear solution. We find the marginal state, where the most unstable linear MRI mode neither grows nor decays, for a set of dimensionless parameters, and then destabilize the system. We examine the system for fiducial parameters comparable to URM07, namely $\Pm = 1.0 \times 10^{-3}$, $\beta = 25$, $q = 1.5$. The system is marginal for a critical wavenumber $k_c = 0.75$ and a critical magnetic Reynolds number $\reym_c = 4.9$.

@@

\section{A. Detailed Equations}\label{app:matrices}

@@

\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & -2 & -\frac{2}{\beta}\partial_x^2 & 0 \\
(2-q)\Omega_0 & 0 & 0 & -\frac{2}{\beta} \\
-1 & 0 & 0 & 0 \\
0 & -1 & q\Omega_0 & 0 \\ \end{matrix}\right] 
\eeq

@@

\beq
\mathcal{L}_3 = \left[\begin{matrix}
0 & 0 & -\frac{2}{\beta} & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix} \right]
\eeq

@@

\beq
\mathcal{G} = \left[\begin{matrix}
0 & 0 & -\frac{2}{\beta}\partial_x^2 & 0 \\
0 & 0 & 0 & -\frac{2}{\beta} \\
-1 & 0 & 0 & 0 \\
0 & -1 & 0 & 0 \\ \end{matrix} \right]
\eeq

@@

\section{B. Expansion of Nonlinear Terms}\label{app:nonlinear_terms}

@@

\beq
N_2^{(\Psi)} = J(\Psi_1, \nabla^2 \Psi_1) \,-\, \frac{2}{\beta}J(A_1, \nabla^2 A_1) 
\eeq

\beq
N_2^{(u)} = J(\Psi_1, u_1) \, - \, \frac{2}{\beta} J(A_1, B_1) 
\eeq

@@

\beq
\begin{split}
N_3^{(\Psi)} & = J(\Psi_1, \nabla^2\Psi_2) \, - \, \frac{2}{\beta}J(A_1, \nabla^2 A_2) \,+\, J(\Psi_2, \nabla^2\Psi_1) - \, \frac{2}{\beta}J(A_2, \nabla^2 A_1) \,+\, 2 J(\Psi_1, \partial_z\partial_Z \Psi_1) \, \\
& - \, 2 \frac{2}{\beta}J(A_1, \partial_z\partial_Z A_1) \,+\, \widetilde{J}(\Psi_1, \nabla^2 \Psi_1) \, - \,  \frac{2}{\beta}\widetilde{J}(A_1, \nabla^2 A_1)\\
\end{split}
\eeq

\beq
N_3^{(u)} = J(\Psi_1, u_2) \, + \, J(\Psi_2, u_1) \, + \, \widetilde{J}(\Psi_1, u_1) \, - \, \frac{2}{\beta} J(A_1, B_2) \, - \, \frac{2}{\beta} J(A_2, B_1) \, - \, \frac{2}{\beta} \widetilde{J}(A_1, B_1)
\eeq

@@

\beq
\begin{split}
N_{22}^{(\Psi)} = & \, i k_c \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11} - k_c^2 \partial_x \Psi_{11}\right) - \partial_x \Psi_{11} \cdot \left(i k_c \partial_x^2 \Psi_{11} - i k_c^3 \Psi_{11}\right) \\
& + \frac{2}{\beta}\partial_x A_{11} \cdot \left(i k_c \partial_x^2 A_{11} - i k_c^3 A_{11}\right) - \frac{2}{\beta} i k_c A_{11} \cdot \left(\partial_x^3 A_{11} - k_c^2 \partial_x A_{11}\right)
\end{split}
\eeq

\beq
\begin{split}
N_{22}^{(u)} = & \, i k_c \Psi_{11} \cdot \partial_x u_{11} - \partial_x \Psi_{11} \cdot i k_c u_{11} - \frac{2}{\beta} i k_c A_{11} \cdot \partial_x B_{11} + \frac{2}{\beta} \partial_x A_{11} \cdot i k_c B_{11}
\end{split}
\eeq

@@

\beq
\begin{split}
N_{20}^{(\Psi)} = & \, i k_c \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11}^* - k_c^2 \partial_x \Psi_{11}^*\right) - \partial_x \Psi_{11} \cdot \left(i k_c^3 \Psi_{11}^* - i k_c \partial_x^2 \Psi_{11}^*\right) \\
& +\frac{2}{\beta} \partial_x A_{11} \cdot \left(i k_c^3 A_{11}^* - i k_c \partial_x^2 A_{11}^* \right) - \frac{2}{\beta} i k_c A_{11} \cdot \left(\partial_x^3 A_{11}^* - k_c^2 \partial_x A_{11}^*\right)
\end{split}
\eeq

\beq
N_{20}^{(u)} = i k_c \Psi_{11} \cdot \partial_x u_{11}^* + \partial_x \Psi_{11} \cdot i k_c u_{11}^* - \frac{2}{\beta} i k_c A_{11} \cdot \partial_x B_{11}^* - \frac{2}{\beta} \partial_x A_{11} \cdot i k_c B_{11}^*
\eeq

@@

\beq
\begin{split}
N_{31}^{(\Psi)} = &  \, i k_c \left(\Psi_{11} \cdot \partial_x^3 \Psi_{20}\right) + i k_c \left(\Psi_{11} \cdot \partial_x^3\Psi_{20}^*\right) - i k_c \left(\Psi_{11}^* \cdot \partial_x^3 \Psi_{22}\right) - i 2 k_c \left(\partial_x \Psi_{11}^* \cdot \partial_x^2 \Psi_{22}\right) \\
& + i 8 k_c^3 \left(\partial_x\Psi_{11}^* \cdot \Psi_{22}\right) + i 4 k_c^3 \left(\Psi_{11}^* \cdot \partial_x \Psi_{22}\right) + \frac{2}{\beta}\left[ - i k_c \left(A_{11} \cdot \partial^3 A_{20}\right) - i k_c \left(A_{11} \cdot \partial_x^3 A_{20}^*\right) \right]\\
& + \frac{2}{\beta}\left[i k_c \left(A_{11}^* \cdot \partial_x^3 A_{22}\right) + i 2 k_c \left(\partial_x A_{11}^* \cdot \partial_x^2 A_{22}\right) - i 8 k_c^3 \left(\partial_x A_{11}^* \cdot A_{22}\right) - i 4 k_c^3 \left(A_{11}^* \cdot \partial_x A_{22}\right)\right] \\
& + i 2 k_c \left(\Psi_{22} \cdot \partial_x^3 \Psi_{11}^*\right) - i 2 k_c^3\left(\Psi_{22} \cdot \partial_x \Psi_{11}^* \right) - i k_c \left(\partial_x \Psi_{20} \cdot \partial_x^2 \Psi_{11}\right) + i k_c \left(\partial_x \Psi_{22} \cdot \partial_x^2 \Psi_{11}^*\right) \\
& - i k_c \left(\partial_x \Psi_{20}^* \cdot \partial_x^2 \Psi_{11}\right) + i k_c^3 \left(\partial_x \Psi_{20} \cdot \Psi_{11}\right) + i k_c^3 \left(\partial_x \Psi_{20}^* \cdot \Psi_{11}\right) - i k_c^3 \left(\partial_x \Psi_{22} \cdot \Psi_{11}^*\right) \\
& + \frac{2}{\beta} \left[ - i 2 k_c \left(A_{22} \cdot \partial_x^3 A_{11}^*\right) + i 2 k_c^3 \left(A_{22} \cdot \partial_x A_{11}^*\right) + i k_c \left(\partial_x A_{20} \cdot \partial_x^2 A_{11}\right) - i k_c \left(\partial_x A_{22} \cdot \partial_x^2 A_{11}^*\right) \right] \\
& + \frac{2}{\beta} \left[ i k_c \left(\partial_x A_{20}^* \cdot \partial_x^2 A_{11}\right) - i k_c^3 \left(\partial_x A_{20} \cdot A_{11}\right) - i k_c^3 \left(\partial_x A_{20}^* \cdot A_{11}\right) + i k_c^3 \left(\partial_x A_{22} \cdot A_{11}^*\right)\right]
\end{split}
\eeq

\beq
\begin{split}
N_{31}^{(u)} = \, & i k_c \left(\Psi_{11} \cdot \partial_x u_{20}\right) + i k_c \left(\Psi_{11} \cdot \partial_x u_{20}^*\right) - i k_c \left(\Psi_{11}^* \cdot \partial_x u_{22}\right) - i 2 k_c \left(\partial_x \Psi_{11}^* \cdot u_{22}\right) \\
& - i k_c \left(u_{11} \cdot \partial_x \Psi_{20} \right) - i k_c \left(u_{11} \cdot \partial_x \Psi_{20}^*\right) + i k_c \left(u_{11}^* \cdot \partial_x \Psi_{22} \right) + i 2 k_c \left(\partial_x u_{11}^* \cdot \Psi_{22}\right) \\
& +\frac{2}{\beta}\left[- i k_c \left(A_{11} \cdot \partial_x B_{20}\right) - i k_c \left(A_{11} \cdot \partial_x B_{20}^*\right) + i k_c \left(A_{11}^* \cdot \partial_x B_{22}\right) + i 2 k_c \left(\partial_x A_{11}^* \cdot B_{22}\right)\right] \\
& +\frac{2}{\beta}\left[ i k_c \left(B_{11} \cdot \partial_x A_{20}\right) + i k_c \left(B_{11} \cdot \partial_x A_{20}^*\right) - i k_c \left(B_{11}^* \cdot \partial_x A_{20}\right) - i 2 k_c \left(\partial_x B_{11}^* \cdot A_{22}\right)\right]
\end{split}
\eeq

@@

\section{C. Linear dispersion relation}\label{app:dispersion}

@@

\appendix
\begin{thebibliography}{}

>>>>

\newcommand\reye{\mathrm{Re}}
\newcommand\reym{\mathrm{Rm}}
\newcommand{\Pm}{\mathrm{Pm}}
\newcommand{\Co}{\mathrm{Co}}

@@

We note several other important analytical studies of MRI saturation. \citeauthor{Knobloch:2005ba} (\citeyear{Knobloch:2005ba}) analyze the MRI in the strongly nonlinear regime, by following the already-developed MRI modes into asymptotic saturation. They consider a thin-gap regime as well, and so their theory may be considered the strongly nonlinear analogue to the one developed here. \citet{Vasil:2015} examines the weakly nonlinear MRI in a thin-gap regime in a minimal model, finding deep mathematical similarities between the MRI system and the elastodynamic instability of a buckling beam. We discuss these results and their relation to ours in section~\ref{sec:discussion}. Several authors have investigated the behavior of the MRI when the boundary conditions are shear periodic, and so the MRI has no mechanism by which to modify the background shear flow profile. In this approximation linear MRI growth is dominated by channel modes, a type of MRI mode that, for periodic boundary conditions, are exact solutions of both the linear and nonlinear MRI equations \citep{Goodman:1994ul}. In this regime the MRI saturates via parasitic instabilities, which feed off and destroy the primary MRI modes. Analytical investigation of this case reveals that MRI saturation can be caused by parasitic Kelvin-Helmholtz and tearing mode instabilities, depending on parameter regime \citep{Pessah:2010ic}. The theory of MRI channel mode parasites is robust \citep[see also][]{Pessah:2009gm,Latter:2010iz,Rembiasz:2016}, but their importance may be overestimated by the local approximation \citep{Latter:2015}, and not germane to global analyses like the one presented here. \citet{Latter:2015} gives a detailed analysis of the relation between local and global linear MRI modes.

@@

We axisymmetrically perturb all three vector components of each of the fluid quantities. We nondimensionalize the equations, with lengths nondimensionalized by $L$, time by $\Omega_0$, velocities by $\Omega_0 L$, magnetic fields by $B_0$, and pressure by $\Omega_0^2 L^2 \rho_0$, where $L$ is the channel width, $\Omega_0$ is the rotation rate at the center of the channel, and $\rho_0$ is the constant pressure in the base state (see Figure \ref{fig:setup}). We define the Reynolds number, $\reye \equiv {\Omega_0 L^2}/{\nu}$, magnetic Reynolds number, $\reym \equiv {\Omega_0 L^2}/{\eta}$, and Cowling number, $\Co \equiv {2 v_A^2}/{\Omega_0^2r_0^2}$, where the Alfv\'en speed $v_A$ is $v_A^2 = {B_0^2}/{\rho_0}$. The fluid symbols $\mathbf{u}$, $\mathbf{B}$, etc. will henceforth be used to refer to the nondimensional, perturbed quantities.
  %a plasma beta parameter, $\beta \equiv {\Omega_0^2r_0^2}/{v_A^2}$, where the Alfv\'en speed $v_A$ is $v_A^2 = {B_0^2}/{\rho_0}$. The fluid symbols $\mathbf{u}$, $\mathbf{B}$, etc. will henceforth be used to refer to the nondimensional, perturbed quantities.

@@

%\begin{widetext}
\onecolumngrid
\beq
\label{eqset1}
\partial_t \nabla^2 \Psi \, - \, 2 \partial_z u_{y} \, - \, \Co B_0 \partial_z \nabla^2 A \, - \, \frac{1}{\reye}\nabla^4 \Psi \, = \, \Co J\left(A, \nabla^2 A \right) \, - \, J\left(\Psi, \nabla^2 \Psi\right) \, 
\eeq
%\end{eqnarray}
%\end{widetext}

\beq
\label{eqset2}
\partial_t u_{y} \, + \, \left(2 - q\right) \Omega_0 \partial_z \Psi \, = \, \Co B_0\partial_z B_{y} \, + \, \Co J\left(A, B_{y}\right) \, - \, J\left(\Psi, u_{y}\right) \, + \, \frac{1}{\reye} \nabla^2 u_{y}
\eeq

@@

The weakly nonlinear regime is where the MRI system is nonlinearly unstable to only the most unstable mode of the linear solution. We find the marginal state, where the most unstable linear MRI mode neither grows nor decays, for a set of dimensionless parameters, and then destabilize the system. We examine the system for fiducial parameters comparable to URM07, namely $\Pm = 1.0 \times 10^{-3}$, $\Co = 0.08$, $q = 1.5$. The system is marginal for a critical wavenumber $k_c = 0.75$ and a critical magnetic Reynolds number $\reym_c = 4.9$.

@@

\section{Detailed Equations}\label{app:matrices}

@@

\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & -2 & -\Co\partial_x^2 & 0 \\
(2-q)\Omega_0 & 0 & 0 & -\Co \\
-1 & 0 & 0 & 0 \\
0 & -1 & q\Omega_0 & 0 \\ \end{matrix}\right] 
\eeq

@@

\beq
\mathcal{L}_3 = \left[\begin{matrix}
0 & 0 & -\Co & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix} \right]
\eeq

@@

\beq
\mathcal{G} = \left[\begin{matrix}
0 & 0 & -\Co\partial_x^2 & 0 \\
0 & 0 & 0 & -\Co \\
-1 & 0 & 0 & 0 \\
0 & -1 & 0 & 0 \\ \end{matrix} \right]
\eeq

@@

\section{Expansion of Nonlinear Terms}\label{app:nonlinear_terms}

@@

\beq
N_2^{(\Psi)} = J(\Psi_1, \nabla^2 \Psi_1) \,-\, \Co J(A_1, \nabla^2 A_1) 
\eeq

\beq
N_2^{(u)} = J(\Psi_1, u_1) \, - \, \Co J(A_1, B_1) 
\eeq

@@

\beq
\begin{split}
N_3^{(\Psi)} & = J(\Psi_1, \nabla^2\Psi_2) \, - \, \Co J(A_1, \nabla^2 A_2) \,+\, J(\Psi_2, \nabla^2\Psi_1) - \, \Co J(A_2, \nabla^2 A_1) \,+\, 2 J(\Psi_1, \partial_z\partial_Z \Psi_1) \, \\
& - \, 2 \Co J(A_1, \partial_z\partial_Z A_1) \,+\, \widetilde{J}(\Psi_1, \nabla^2 \Psi_1) \, - \,  \Co \widetilde{J}(A_1, \nabla^2 A_1)\\
\end{split}
\eeq

\beq
N_3^{(u)} = J(\Psi_1, u_2) \, + \, J(\Psi_2, u_1) \, + \, \widetilde{J}(\Psi_1, u_1) \, - \, \Co J(A_1, B_2) \, - \, \Co J(A_2, B_1) \, - \, \Co \widetilde{J}(A_1, B_1)
\eeq

@@

\beq
\begin{split}
N_{22}^{(\Psi)} = & \, i k_c \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11} - k_c^2 \partial_x \Psi_{11}\right) - \partial_x \Psi_{11} \cdot \left(i k_c \partial_x^2 \Psi_{11} - i k_c^3 \Psi_{11}\right) \\
& + \Co \partial_x A_{11} \cdot \left(i k_c \partial_x^2 A_{11} - i k_c^3 A_{11}\right) - \Co i k_c A_{11} \cdot \left(\partial_x^3 A_{11} - k_c^2 \partial_x A_{11}\right)
\end{split}
\eeq

\beq
\begin{split}
N_{22}^{(u)} = & \, i k_c \Psi_{11} \cdot \partial_x u_{11} - \partial_x \Psi_{11} \cdot i k_c u_{11} - \Co i k_c A_{11} \cdot \partial_x B_{11} + \Co \partial_x A_{11} \cdot i k_c B_{11}
\end{split}
\eeq

@@

\beq
\begin{split}
N_{20}^{(\Psi)} = & \, i k_c \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11}^* - k_c^2 \partial_x \Psi_{11}^*\right) - \partial_x \Psi_{11} \cdot \left(i k_c^3 \Psi_{11}^* - i k_c \partial_x^2 \Psi_{11}^*\right) \\
& + \Co \partial_x A_{11} \cdot \left(i k_c^3 A_{11}^* - i k_c \partial_x^2 A_{11}^* \right) - \Co i k_c A_{11} \cdot \left(\partial_x^3 A_{11}^* - k_c^2 \partial_x A_{11}^*\right)
\end{split}
\eeq

\beq
N_{20}^{(u)} = i k_c \Psi_{11} \cdot \partial_x u_{11}^* + \partial_x \Psi_{11} \cdot i k_c u_{11}^* - \Co i k_c A_{11} \cdot \partial_x B_{11}^* - \Co \partial_x A_{11} \cdot i k_c B_{11}^*
\eeq

@@

\beq
\begin{split}
N_{31}^{(\Psi)} = &  \, i k_c \left(\Psi_{11} \cdot \partial_x^3 \Psi_{20}\right) + i k_c \left(\Psi_{11} \cdot \partial_x^3\Psi_{20}^*\right) - i k_c \left(\Psi_{11}^* \cdot \partial_x^3 \Psi_{22}\right) - i 2 k_c \left(\partial_x \Psi_{11}^* \cdot \partial_x^2 \Psi_{22}\right) \\
& + i 8 k_c^3 \left(\partial_x\Psi_{11}^* \cdot \Psi_{22}\right) + i 4 k_c^3 \left(\Psi_{11}^* \cdot \partial_x \Psi_{22}\right) + \Co \left[ - i k_c \left(A_{11} \cdot \partial^3 A_{20}\right) - i k_c \left(A_{11} \cdot \partial_x^3 A_{20}^*\right) \right]\\
& + \Co \left[i k_c \left(A_{11}^* \cdot \partial_x^3 A_{22}\right) + i 2 k_c \left(\partial_x A_{11}^* \cdot \partial_x^2 A_{22}\right) - i 8 k_c^3 \left(\partial_x A_{11}^* \cdot A_{22}\right) - i 4 k_c^3 \left(A_{11}^* \cdot \partial_x A_{22}\right)\right] \\
& + i 2 k_c \left(\Psi_{22} \cdot \partial_x^3 \Psi_{11}^*\right) - i 2 k_c^3\left(\Psi_{22} \cdot \partial_x \Psi_{11}^* \right) - i k_c \left(\partial_x \Psi_{20} \cdot \partial_x^2 \Psi_{11}\right) + i k_c \left(\partial_x \Psi_{22} \cdot \partial_x^2 \Psi_{11}^*\right) \\
& - i k_c \left(\partial_x \Psi_{20}^* \cdot \partial_x^2 \Psi_{11}\right) + i k_c^3 \left(\partial_x \Psi_{20} \cdot \Psi_{11}\right) + i k_c^3 \left(\partial_x \Psi_{20}^* \cdot \Psi_{11}\right) - i k_c^3 \left(\partial_x \Psi_{22} \cdot \Psi_{11}^*\right) \\
& + \Co \left[ - i 2 k_c \left(A_{22} \cdot \partial_x^3 A_{11}^*\right) + i 2 k_c^3 \left(A_{22} \cdot \partial_x A_{11}^*\right) + i k_c \left(\partial_x A_{20} \cdot \partial_x^2 A_{11}\right) - i k_c \left(\partial_x A_{22} \cdot \partial_x^2 A_{11}^*\right) \right] \\
& + \Co \left[ i k_c \left(\partial_x A_{20}^* \cdot \partial_x^2 A_{11}\right) - i k_c^3 \left(\partial_x A_{20} \cdot A_{11}\right) - i k_c^3 \left(\partial_x A_{20}^* \cdot A_{11}\right) + i k_c^3 \left(\partial_x A_{22} \cdot A_{11}^*\right)\right]
\end{split}
\eeq

\beq
\begin{split}
N_{31}^{(u)} = \, & i k_c \left(\Psi_{11} \cdot \partial_x u_{20}\right) + i k_c \left(\Psi_{11} \cdot \partial_x u_{20}^*\right) - i k_c \left(\Psi_{11}^* \cdot \partial_x u_{22}\right) - i 2 k_c \left(\partial_x \Psi_{11}^* \cdot u_{22}\right) \\
& - i k_c \left(u_{11} \cdot \partial_x \Psi_{20} \right) - i k_c \left(u_{11} \cdot \partial_x \Psi_{20}^*\right) + i k_c \left(u_{11}^* \cdot \partial_x \Psi_{22} \right) + i 2 k_c \left(\partial_x u_{11}^* \cdot \Psi_{22}\right) \\
& +\Co \left[- i k_c \left(A_{11} \cdot \partial_x B_{20}\right) - i k_c \left(A_{11} \cdot \partial_x B_{20}^*\right) + i k_c \left(A_{11}^* \cdot \partial_x B_{22}\right) + i 2 k_c \left(\partial_x A_{11}^* \cdot B_{22}\right)\right] \\
& + \Co \left[ i k_c \left(B_{11} \cdot \partial_x A_{20}\right) + i k_c \left(B_{11} \cdot \partial_x A_{20}^*\right) - i k_c \left(B_{11}^* \cdot \partial_x A_{20}\right) - i 2 k_c \left(\partial_x B_{11}^* \cdot A_{22}\right)\right]
\end{split}
\eeq

@@

\section{Linear dispersion relation}\label{app:dispersion}

@@

%\appendix
\begin{thebibliography}{}
